From Likes to Change: Assessing the Impact of Citizen Engagement on the European

### 2023-06-14 Article.Rmd
Final paper

Despite these findings, the study is not without limitations. The low R^2 values in our regression models indicate that other unexamined variables might have significant effects on public engagement levels. Future research should persist in exploring these potential factors, acknowledging the complex and multifaceted nature of engagement behaviors.

Additionally, the scope of this research was confined to the European Commission's use of four primary social media platforms. Future inquiries could potentially explore other platforms or public institutions to determine the universality of the observed patterns. Furthermore, while our focus lay primarily on emotional resonance, future research could delve into other aspects of communication, such as tone, complexity, and framing.

>>>>

Despite these findings, the study is not without limitations. The scope of this research was confined to the European Commission's use of four primary social media platforms. Future inquiries could potentially explore other platforms or public institutions to determine the universality of the observed patterns. Furthermore, while our focus lay primarily on emotional resonance, future research could delve into other aspects of communication, such as tone, complexity, and framing.

This research has also limitations due to the use of secondary data obtained from platforms, suggesting future studies could benefit from primary data collection. Additionally, this study did not associate Engagement Rate (ER) with significant concurrent events, potentially overlooking the impact of emotional reactions based on these events. Future studies could explore these associations to understand emotional impacts better, thus extending the existing knowledge in the field.
